### 2019-08-13 report/chapter03.Rnw
Corrected version, discussion, introduction

The sample sizes among results vary to some extent. There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, 95\% smaller than \Sexpr{treatment.group.size.range[6]}. The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{treatment.group.size.range[5]} and the third quartile \Sexpr{treatment.group.size.range[4]}. The large difference between median and mean is caused by very large groups with over 2,000,000 participants. Analogously, the quantiles of the total sample size are: 5\% quantile = \Sexpr{samplesize.range[1]}, first quartile = \Sexpr{samplesize.range[2]}, median = \Sexpr{samplesize.range[3]}, third quartile = \Sexpr{samplesize.range[4]} and 95\% = \Sexpr{samplesize.range[6]}. The mean is \Sexpr{samplesize.range[5]}. \\
There are \Sexpr{comp.range[1]} reviews with five or fewer results. The 5\% and 95\% quantiles are \Sexpr{comp.range[7]} and \Sexpr{comp.range[6]}. The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}. Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]} and the 95\% quantile \Sexpr{study.range[6]}. The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citet{largest.review} 
which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1,497 results in total.\\
For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome. The studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis. This distinction is also used by the Cochrane Organization itself, \ie the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.

@@

Meta-analysis groups within a review were obtained by grouping by comparison, outcome and subgroup. The last step is optional, and the Cochrane groups do also meta-analysis without taking into account subgroups. Subgroups are often specifications of treatment, \eg the form of the medication or the protocol. Thus, using the subgroups should increase the within-study homogeneity. However, the Cochrane Organisation disencourages meta-analyses based on subgroups only, because subgroups are often set up after the collection of the data analysis. Since the main interest of this study is not to precisely assess the efficacy of treatments, but the interest is merely on systematic differences between single studies investigating the same scientific question and not in the effect per se, it has been decided that the increase in precision is worthwhile the loss of a number of studies. While it is possible that the use of subgroups introduces bias in the meta-analysis, it is also possible that ignoring subgroups will do (which is one of the reasons why subgroups are analyses as well). When one subgroup has substantially different real treatment effects, and the specific properties influence study size, publication bias assessment fails. Subgroups are not indicated in \Sexpr{no.subgroup}\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane review groups did.

>>>>

The sample sizes among results vary to some extent. There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, 95\% smaller than \Sexpr{treatment.group.size.range[6]}. The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{treatment.group.size.range[5]} and the third quartile \Sexpr{treatment.group.size.range[4]}. The large difference between median and mean is caused by very large groups with over 2,000,000 participants. Analogously, the quantiles of the total sample size are: 5\% quantile = \Sexpr{samplesize.range[1]}, first quartile = \Sexpr{samplesize.range[2]}, median = \Sexpr{samplesize.range[3]}, third quartile = \Sexpr{samplesize.range[4]} and 95\% = \Sexpr{samplesize.range[6]}. The mean is \Sexpr{samplesize.range[5]}. \\
There are \Sexpr{comp.range[1]} reviews with five or fewer results. The 5\% and 95\% quantiles are \Sexpr{comp.range[7]} and \Sexpr{comp.range[6]}. The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}. Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]} and the 95\% quantile \Sexpr{study.range[6]}. The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citet{largest.review} 
which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1,497 results in total.\\
For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome. The studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis. This distinction is also used by Cochrane, \ie the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.

@@

Meta-analysis groups within a review were obtained by grouping by comparison, outcome and subgroup. The last step is optional, and the Cochrane Groups do also meta-analysis without taking into account subgroups. Subgroups are often specifications of treatment, \eg the form of the medication or the protocol. Thus, using the subgroups should increase the within-study homogeneity. However, the Cochrane disencourages meta-analyses based on subgroups only, because subgroups are often set up after the collection of the data analysis. Since the main interest of this study is not to precisely assess the efficacy of treatments, but the interest is merely on systematic differences between single studies investigating the same scientific question and not in the effect per se, it has been decided that the increase in precision is worthwhile the loss of a number of studies. While it is possible that the use of subgroups introduces bias in the meta-analysis, it is also possible that ignoring subgroups will do (which is one of the reasons why subgroups are analyses as well). When one subgroup has substantially different real treatment effects, and the specific properties influence study size, publication bias assessment fails. Subgroups are not indicated in \Sexpr{no.subgroup}\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane Review Groups did.
